Status of nuclear optical potentials and future prospects

### 2019-07-05 Notes/Candidacy/Paper/candidacy_paper.tex
Updates to candidacy notes
Changed the sub-section headers.
Updates to candidacy paper
Adding more to candidacy paper outline.

Things to include:
\\
-- Why are nuclear reactions important? (Processes that help us understand nuclear structure amongst other things.) List examples.
\\
-- How do optical potentials help us understand nuclear reactions?
\\
-- r-process for motivation.
\\
-- Include multiple scattering, self-consistent Green's function methods.
\\
-- Should probably have a basic formalism section before going into phenomenology.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Phenomenology of optical potentials}
\label{sec:section_2}

Things to include:
\\
-- Form of the potential: Woods-Saxon shape, coulomb component, spin-orbit force.
\\
-- Fit strength, radii, and diffuseness of complex potential.
\\
-- Issue: fitting ambiguities, extractions to exotic regions of the nuclear chart.
\\
-- Make sure to touch on phenomenology of optical potentials in modern experimental analyses (key word is modern!)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Ab initio optical potentials} % See how papers would refer to this "microscopic"
\label{sec:section_3}

Things to include:
\\
-- Successes and limitations.
\\
-- Motivation: predictions for exotic region of the nuclear chart.
\\
-- Coupled cluster Green's function \cite{Rotureau:2016jpf}.

@@

Things to include:
\\
-- Fitting ambiguities for phenomenological potential.
\\
-- Uncertainty quantification.
\\
-- Add this to outlook in conclusion?

@@

\bibliography{../tropiano_bib}

>>>>

Things to include:
\\
-- Why are nuclear reactions important? (Processes that help us understand nuclear structure amongst other things.) List examples.
\\
-- r-process for motivation.
\\
-- How do optical potentials help us understand nuclear reactions?
\\
-- References: ...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formalism}
\label{sec:formalism}

Things to include:
\\
-- More general things from Thompson/Nunes: define optical potentials as complex potentials and consequences of this. Reaction cross section derivation.
\\
-- Derivation of the general optical potential (equation (2.15) in Feshbach).
\\
-- Properties of the potential: complex (meaning), non-local (derivation), dispersion relation.
\\
-- Relation to observables (basic quantum stuff?)
\\
-- References: \cite{Feshbach:1958nx}, \cite{Feshbach:1962ut}, Thompson/Nunes textbook (73, 126).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Phenomenology}
\label{sec:phenomenology}

Things to include:
\\
-- Form of the potential: Woods-Saxon shape, coulomb component, spin-orbit force. (Basic example in Thompson/Nunes.). Can start with discussion similar to Thompson/Nunes.
\\
-- Fit strength, radii, and diffuseness of complex potential.
\\
-- Issue: fitting ambiguities, extractions to exotic regions of the nuclear chart.
\\
-- Make sure to touch on phenomenology of optical potentials in modern experimental analyses (key word is modern!)
\\
-- References: \cite{Dickhoff:2018wdd} section 3, \cite{Koning:2003zz}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Microscopic optical potentials}
\label{sec:microscopic}

Things to include:
\\
-- Successes and limitations.
\\
-- Motivation: predictions for exotic region of the nuclear chart.
\\
-- Coupled cluster Green's function \cite{Rotureau:2016jpf}.
\\
-- References: \cite{Dickhoff:2018wdd} section 4, \cite{Furumoto:2019anr} G-matrix interaction, \cite{Idini:2019hkq} self-consistent Green's function, \cite{Rotureau:2016jpf}.

@@

Things to include:
\\
-- Fitting ambiguities for phenomenological potential.
\\
-- Uncertainty quantification.
\\
-- Add this to outlook in conclusion?
\\
-- References: \cite{King:2018vzw}.

@@

\bibliography{../../tropiano_bib}
